%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}
\title{Resume}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{10pt}
\namesection{Ian}{Stanton}{ \href{mailto:user@example.com}{stant099@umn.edu} | 1160 Tonkawa Road, Orono, MN 55356 | (952)288-4099
}

\href{https://www.linkedin.com/in/istanton/}{https://www.linkedin.com/in/istanton/}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\topsep}
Engineering professional with experience in the health care technology industry. Computer Science graduate with a passion for understanding the mechanics of hardware and software on a detailed level. Desire to apply my skills and experiences to the design, development and creation of meaningful products that directly affect the lives of others in a positive manner.

\section{Experience}

\runsubsection{UnitedHealth Group}
\descript{| Optum | Minneapolis, MN}
\location{Data Scientist II | January 2017 - Present}
\vspace{\topsep} 
\begin{tightemize}
% PROJECTS
\item Project Involvement
    \vspace{\topsep}
    \begin{tightemize}
    \item Served as technical lead in automating a manual process for reviewing health insurance claims.
    % Created a method, based on machine learning,...
    \item Performed data extraction and transformation for machine learning projects, including models used to impute a medical diagnosis based on a patient's pharmacy data.
    \item Configured and utilized entity resolution software to identify insurance fraud and enterprise-wide fraudulent activity.
    \item Contributed to the design and implementation of Fossology Open Source License Compliance scanner.  Used as a standalone Git repository scanner or integrated as a Jenkins pipeline procedure.
    \end{tightemize}
    \vspace{\topsep}
% \item Led team of data scientists in an effort to improve a very manual process for reviewing insurance claims.
% \item Worked on machine learning project focused on imputing a medical diagnosis based on a patient's pharmacy data.  Models were created for 60+ diseases / conditions, including Depression, Hypertension, and ADHD.
% INFRASTRUCTURE
\item Infrastructure
    \vspace{\topsep}
    \begin{tightemize}
    \item Designed, implemented and maintained core components of the data science team's infrastructure.
    \item Built data pipeline monitoring and scheduling platform using Apache Airflow.
    \item Built Linux server \& database monitoring system using Grafana.
    \item Provided a secure, containerized data science work environment utilizing Docker, Jupyter, Mesos and Marathon.
    \item Created and maintained encryption key management server using Docker, HashiCorp Vault and OpenShift.
    \item Configured application \& server log pipeline using Elastic Stack (Filebeat, Logstash, Elasticsearch, Kibana)
    \end{tightemize}
    \vspace{\topsep}
% MICROSERVICES
\item Microservices
    \vspace{\topsep}
    \begin{tightemize}
    \item Developed process using Docker and OpenShift for deploying machine learning models for customer use.
    \end{tightemize}
    \vspace{\topsep}
% PROCESS IMPROVEMENT
\item Process Improvement
    \vspace{\topsep}
    \begin{tightemize}
    \item Defined and implemented proper coding and version control standards for projects.
    \item Promoted regular code reviews to ensure these standards were being followed.
    \end{tightemize}
    \vspace{\topsep}
\end{tightemize}
\sectionsep

%\runsubsection{Optum}
%\descript{| Endpoint Sensitive Data Protection }
\location{Endpoint Sensitive Data Protection | June 2016 – January 2017}
\vspace{\topsep} 
\begin{tightemize}
\item Drove enterprise wide process to scan desktops for sensitive data (PHI/PII/PCI) using Symantec Data Loss Prevention tool.
\item Developed process for testing and tuning Symantec's Data Loss Prevention tool.
\item Ensured that the services, methods, and requirements of the Endpoint Sensitive Data Protection (ESDP) program were well documented, communicated, and understood by our stakeholders and partners.
\end{tightemize}
\sectionsep

%\runsubsection{Optum}
%\descript{| Intern - Cyber Forensic Investigations}
\location{Intern - Cyber Forensic Investigations | May 2015 - August 2015}
\vspace{\topsep} 
\begin{tightemize}
\item Improved compatibility of EnScript used to scan devices within the company.
\item Led testing and evaluation of third party forensic tool.
\item Performed research and provided insight on big data platforms for Security Big Data Lake.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\runsubsection{University of Minnesota}
\descript{| Bachelor of Computer Science}
\location{May 2016 | Minneapolis, MN}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TECHNICAL SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}
\begin{minipage}[t]{.6\textwidth}
\subsection{Programming Languages}
Python \textbullet{}   C/C++ \textbullet{} Bash \\
SQL \textbullet{} Java \textbullet{} R \\
Markdown \textbullet{} \LaTeX\ \textbullet{} OCaml \\
\sectionsep
\end{minipage}
\hfill
\begin{minipage}[t]{.35\textwidth}
\subsection{Software \& Tools}
Linux \textbullet{} Docker \textbullet{} OpenShift\\
Elastic Stack \textbullet{} Apache Airflow\\
Relational Database Management Systems\\
Git \textbullet{} Mesos \textbullet{} Spark \textbullet{} Hadoop\\
Amazon Web Services \textbullet{} Microsoft Azure\\
Splunk  \textbullet{} Sqoop\\
\end{minipage}

\end{document}  \documentclass[]{article}